---
title       : Panama's Goverment Payroll Distribution
subtitle    : 
author      : Ivan Barria
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : [bootstrap]            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Panama's Goverment Payroll Distribution

Since forever, governmental entities have been plagued by inneptitude and mediocrity.
My theory is that this is due to the fact that the government underpays mosts of their employees and thus can only hire incompetent people.

--- .class #id 

## Getting the Data

I had to write a scaper using python3.
https://github.com/LaPrensa/defensoria-planilla

It uses asyncio :)

---

## Processing the Data

The data was exported to CSV using the \copy command from postgresql.

```{r}
df <- read.csv('planilla.csv')
df$institucion <- as.factor(df$institucion)
df$salario <- as.numeric(gsub(',','',df$salario))
```

---

## General Overview

```{r}
library(ggplot2)
qplot(df$salario)
```

---

## Bad Distribution

Notice the large spread.

```{r}
summary(df$salario)
```

As expected, there are alot of low paying jobs.

---

## Breakdown by Government Entity

If you would like a breakdown by government entity then visit my shinyapp
http://ibarria.shinyapps.io/defensoria/
